---
title: "Bai_Xin_HW1"
author: "xbai15"
date: "9/17/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# **Introduction**
This R Markdown document is the analyzation of *employee_attrition.csv* dataset. <br>The goal is to find out and present the most interesting and significant rules which could predict *`Attrition`*.

### Information of Dataset
This data set presents an employee survey from IBM, indicating if there is attrition or not. It consist of 1176 observations and 35 variables.

### Information of Variables
##### *Numerical Variables*

| Variables | Type | Missing Counts | Min | Median | Mean | Max |
|----------------|----------------|----------------|----------------|----------------|----------------|----------------|
|   $Age$ | int | 0 | 18 | 36 | 36 | 60 |
|   $DailyRate$ | int | 0 | 796 | 800 | 36 | 60 |
|   $DistanceFromHome$ | int | 2 | 1 | 7 | 9.5 | 224 |
|   $Education$ | int | 0 | 1 | 3 | 2.9 | 5 |
|   $EmployeeCount$ | int | 0 | 1 | 1 | 1 | 1 |
|   $EmployeeNumber$ | int | 0 | 1 | 1032.5 | 1036.4 | 2068 |
|   $EnvironmentSatisfaction$ | int | 0 | 1 | 3 | 2.7 | 4 |
|   $HourlyRate$ | int | 0 | 30 | 66 | 65.8 | 100 |
|   $JobInvolvement$ | int | 0 | 1 | 3 | 2.7 | 4 |
|   $JobLevel$ | int | 1 | 1 | 2 | 2.1 | 5 |
|   $JobSatisfaction$ | int | 0 | 1 | 3 | 2.7 | 4 |
|   $MonthlyIncome$ | int | 0 | 1009 | 4950 | 6526 | 19973 |
|   $MonthlyRate$ | int | 0 | 2094 | 14488 | 14468 | 26999 |
|   $NumCompaniesWorked$ | int | 0 | 0 | 2 | 2.7 | 9 |
|   $PercentSalaryHike$ | int | 1 | 11 | 14 | 15.3 | 25 |
|   $RelationshipSatisfaction$ | int | 1 | 3 | 3 | 3.2 | 4 |
|   $StandardHours$ | int | 0 | 80 | 80 | 80 | 80 |
|   $StockOptionLevel$ | int | 0 | 0 | 1 | 0.8 | 3 |
|   $TotalWorkingYears$ | int | 2 | 0 | 10 | 11.4 | 114 |
|   $TrainingTimeLastYear$ | int | 0 | 0 | 3 | 2.8 | 6 |
|   $WorkLifeBalance$ | int | 0 | 1 | 3 | 2.7 | 4 |
|   $YearsAtCompany$ | int | 0 | 0 | 5 | 6.9 | 40 |
|   $YearsInCurrentRole$ | int | 0 | 0 | 3 | 4.2 | 18 |
|   $YearsSinceLastPromotion$ | int | 1 | 0 | 1 | 2.1 | 15 |
|   $YearsWithCurrManager$ | int | 0 | 0 | 3 | 4.2 | 219 |

##### *Categorical Variables*

| Variables | Type | Missing Counts | Unique Counts |
|----------------------------|--------------------------------------------|----------------------------|----------------------------|
|   $Attrition$ | chr | 0 | 2 |
|   $BusinessTravel$ | chr | 0 | 3 |
|   $Department$ | chr | 0 | 3 |
|   $EducationField$ | chr | 0 | 6 |
|   $Gender$ | chr | 0 | 2 |
|   $JobRole$ | chr | 0 | 9 |
|   $MaritalStatus$ | chr | 0 | 3 |
|   $Over18$ | chr | 0 | 1 |
|   $OverTime$ | chr | 0 | 3 |


# **Exploratory Data Analysis(EDA)**
### Data Cleaning
##### Columns w/ NA

```{r, echo = FALSE}

library(knitr)
library(arules)
library(arulesViz)

ea <- read.csv("https://raw.githubusercontent.com/xbai15/IST707-HW1/master/employee_attrition.csv?token=AQV5GHX24J6LREOIDR7BFTC7M4DDQ")

```

```{r}

colnames(ea)[colSums((is.na(ea)))>0]

```

DistanceFromHome
```{r}

ea$DistanceFromHome[is.na(ea$DistanceFromHome)] <- mean(ea$DistanceFromHome, na.rm = TRUE)

```

Gender
```{r}

ea$Gender[is.na(ea$Gender)]<-rownames(sort((table(ea$Gender)),decreasing = TRUE))[1]

```

JobLevel
```{r}

ea$JobLevel[is.na(ea$JobLevel)] <- mean(ea$JobLevel, na.rm = TRUE)

```

OverTime
```{r}

ea$OverTime[is.na(ea$OverTime)]<-rownames(sort((table(ea$OverTime)),decreasing = TRUE))[1]

```

PercentSalaryHike
```{r}

ea$PercentSalaryHike[is.na(ea$PercentSalaryHike)] <- mean(ea$PercentSalaryHike, na.rm = TRUE)

```

PerformanceRating
```{r}

ea$PerformanceRating[is.na(ea$PerformanceRating)] <- mean(ea$PerformanceRating, na.rm = TRUE)

```

RelationshipSatisfaction
```{r}

ea$RelationshipSatisfaction[is.na(ea$RelationshipSatisfaction)] <- mean(ea$RelationshipSatisfaction, na.rm = TRUE)

```

TotalWorkingYears
```{r}

ea$TotalWorkingYears[is.na(ea$TotalWorkingYears)] <- mean(ea$TotalWorkingYears, na.rm = TRUE)

```

YearsSinceLastPromotion
```{r}

ea$YearsSinceLastPromotion[is.na(ea$YearsSinceLastPromotion)] <- mean(ea$YearsSinceLastPromotion, na.rm = TRUE)

```

Check NA now
```{r}

colnames(ea)[colSums((is.na(ea)))>0]

```

##### Remove Columns w/ constant value
Remove "Employee Count" "Over18" "StandardHours" "EmployeeNumber"
```{r}

ea <- within(ea, rm("EmployeeCount", "Over18", "StandardHours", "EmployeeNumber"))

```

## Visualization {.tabset .tabset-pills}
### Age
```{r, echo = FALSE}

ea <- read.csv("https://raw.githubusercontent.com/xbai15/IST707-HW1/master/employee_attrition.csv?token=AQV5GHX24J6LREOIDR7BFTC7M4DDQ")


hist(ea$Age, col = "#4AA4DE",breaks = 40, main = "Employee Age Distribution", xlab = "Age", border = FALSE)

barplot(table(ea$Attrition,ea$Age), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Age", ylab = "Attrition", main = "Attrition base on Employee Age")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Business Travel
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$BusinessTravel), aes(x=ea$BusinessTravel)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Business Travel Distribution") +xlab("Business Travel")

dat <- data.frame(table(ea$BusinessTravel,ea$Attrition))
names(dat) <- c("BusinessTravel", "Attrition", "Count")
ggplot(data = dat, aes(x = BusinessTravel, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Business Travel") +xlab("Business Travel")
```

### Daily Rate
```{r, echo = FALSE}

hist(ea$DailyRate, col = "#4AA4DE",breaks = 100, main = "Employee Daily Rate Distribution", xlab = "Daily Rate", border = FALSE)

barplot(table(ea$Attrition,ea$DailyRate), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Daily Rate", ylab = "Attrition", main = "Attrition base on Employee Daily Rate")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Department
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$Department), aes(x=ea$Department)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Department Distribution") +xlab("Department")

dat <- data.frame(table(ea$Department,ea$Attrition))
names(dat) <- c("Department", "Attrition", "Count")
ggplot(data = dat, aes(x = Department, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Department") +xlab("Department")
```


### Distance From Home
```{r, echo = FALSE}

hist(ea$DistanceFromHome, col = "#4AA4DE",breaks = 200, main = "Employee Distance from home Distribution", xlab = "Distance from home", border = FALSE)

barplot(table(ea$Attrition,ea$DistanceFromHome), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Distance from home", ylab = "Attrition", main = "Attrition base on Employee Distance from home")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```


Note: There is a abnormally large value 224 in this column.

We made a assumption that the 224 was a typo and it's suppose to be 24
```{r}

sort(ea$DistanceFromHome, decreasing = TRUE)[1]

ea$DistanceFromHome[ea$DistanceFromHome == 224] <- 24

```


### Education
```{r, echo = FALSE}

hist(ea$Education, col = "#4AA4DE",breaks = 5, main = "Employee Education Distribution", xlab = "Education", border = FALSE)

barplot(table(ea$Attrition,ea$Education), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Education", ylab = "Attrition", main = "Attrition base on Employee Education")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Education Field
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$EducationField), aes(x=ea$EducationField)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Education Field Distribution") +xlab("Education Field")

dat <- data.frame(table(ea$EducationField,ea$Attrition))
names(dat) <- c("EducationField", "Attrition", "Count")
ggplot(data = dat, aes(x = EducationField, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Education Field") +xlab("Education Field")
```

### Environment Satisfaction
```{r, echo = FALSE}

hist(ea$EnvironmentSatisfaction, col = "#4AA4DE",breaks = 5, main = "Employee Environment Satisfaction Distribution", xlab = "Environment Satisfaction", border = FALSE)

barplot(table(ea$Attrition,ea$EnvironmentSatisfaction), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Environment Satisfaction", ylab = "Attrition", main = "Attrition base on Employee Environment Satisfaction")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Gender
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$Gender), aes(x=ea$Gender)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Gender Distribution") +xlab("Gender")

dat <- data.frame(table(ea$Gender,ea$Attrition))
names(dat) <- c("Gender", "Attrition", "Count")
ggplot(data = dat, aes(x = Gender, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Gender") +xlab("Gender")
```

### Hourly Rate
```{r, echo = FALSE}

hist(ea$HourlyRate, col = "#4AA4DE",breaks = 100, main = "Employee Hourly Rate Distribution", xlab = "Hourly Rate", border = FALSE)

barplot(table(ea$Attrition,ea$HourlyRate), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Hourly Rate", ylab = "Attrition", main = "Attrition base on Employee Hourly Rate")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Job Involvement
```{r, echo = FALSE}

hist(ea$JobInvolvement, col = "#4AA4DE",breaks = 5, main = "Employee Job Involvement Distribution", xlab = "Job Involvement", border = FALSE)

barplot(table(ea$Attrition,ea$JobInvolvement), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Job Involvement", ylab = "Attrition", main = "Attrition base on Employee Job Involvement")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Job Level
```{r, echo = FALSE}

hist(ea$JobLevel, col = "#4AA4DE",breaks = 5, main = "Employee Job Level Distribution", xlab = "Job Level", border = FALSE)

barplot(table(ea$Attrition,ea$JobLevel), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Job Level", ylab = "Attrition", main = "Attrition base on Employee Job Level")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Job Role
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$JobRole), aes(x=ea$JobRole)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Job Role Distribution") +xlab("Job Role") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

dat <- data.frame(table(ea$JobRole,ea$Attrition))
names(dat) <- c("JobRole", "Attrition", "Count")
ggplot(data = dat, aes(x = JobRole, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Job Role") +xlab("Job Role") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Job Satisfaction
```{r, echo = FALSE}

hist(ea$JobSatisfaction, col = "#4AA4DE",breaks = 5, main = "Employee Job Satisfaction Distribution", xlab = "Job Satisfaction", border = FALSE)

barplot(table(ea$Attrition,ea$JobSatisfaction), col = c("#4AA4DE","gray"), border = FALSE,xlab = "Job Satisfaction", ylab = "Attrition", main = "Attrition base on Employee Job Satisfaction")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Marital Status
```{r, echo = FALSE}
library(ggplot2)

ggplot(data.frame(ea$MaritalStatus), aes(x=ea$MaritalStatus)) +
  geom_bar(fill = "#4AA4DE") + theme_classic() + ggtitle("Employee Marital Status Distribution") +xlab("Marital Status")

dat <- data.frame(table(ea$MaritalStatus,ea$Attrition))
names(dat) <- c("MaritalStatus", "Attrition", "Count")
ggplot(data = dat, aes(x = MaritalStatus, y = Count, fill = Attrition)) + geom_bar(stat = "identity")+ scale_fill_manual(values = c("#4AA4DE","gray")) + theme_classic() + ggtitle("Attrition base on Employee Marital Status") +xlab("Marital Status")
```

### Monthly Income
```{r, echo = FALSE}

hist(ea$MonthlyIncome, col = "#4AA4DE",breaks = 100, main = "Employee Monthly Income Distribution", xlab = "Monthly Income", border = FALSE)

barplot(table(ea$Attrition,ea$MonthlyIncome), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Monthly Income", ylab = "Attrition", main = "Attrition base on Employee Monthly Income")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Monthly Rate
```{r, echo = FALSE}

hist(ea$MonthlyRate, col = "#4AA4DE",breaks = 100, main = "Employee Monthly Rate Distribution", xlab = "Monthly Rate", border = FALSE)

barplot(table(ea$Attrition,ea$MonthlyRate), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Monthly Rate", ylab = "Attrition", main = "Attrition base on Employee Monthly Rate")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Number of Companies Worked
```{r, echo = FALSE}

hist(ea$NumCompaniesWorked, col = "#4AA4DE",breaks = 10, main = "Employee Number of Companies Worked Distribution", xlab = "Number of Companies Worked", border = FALSE)

barplot(table(ea$Attrition,ea$NumCompaniesWorked), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Number of Companies Worked", ylab = "Attrition", main = "Attrition base on Employee Number of Companies Worked")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Percent Salary Hike
```{r, echo = FALSE}

hist(ea$PercentSalaryHike, col = "#4AA4DE",breaks = 15, main = "Employee Percent Salary Hike Distribution", xlab = "Percent Salary Hike", border = FALSE)

barplot(table(ea$Attrition,ea$PercentSalaryHike), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Percent Salary Hike", ylab = "Attrition", main = "Attrition base on Employee Percent Salary Hike")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Performance Rating
```{r, echo = FALSE}

hist(ea$PerformanceRating, col = "#4AA4DE",breaks = 2, main = "Employee Performance Rating Distribution", xlab = "Performance Rating", border = FALSE)

barplot(table(ea$Attrition,ea$PerformanceRating), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Performance Rating", ylab = "Attrition", main = "Attrition base on Employee Performance Rating")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Relationship Satisfaction
```{r, echo = FALSE}

hist(ea$RelationshipSatisfaction, col = "#4AA4DE",breaks = 5, main = "Employee Relationship Satisfaction Distribution", xlab = "Relationship Satisfaction", border = FALSE)

barplot(table(ea$Attrition,ea$RelationshipSatisfaction), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Relationship Satisfaction", ylab = "Attrition", main = "Attrition base on Employee Relationship Satisfaction")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Stock Option Level
```{r, echo = FALSE}

hist(ea$StockOptionLevel, col = "#4AA4DE",breaks = 5, main = "Employee Stock Option Level Distribution", xlab = "Stock Option Level", border = FALSE)

barplot(table(ea$Attrition,ea$StockOptionLevel), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Stock Option Level", ylab = "Attrition", main = "Attrition base on Employee Stock Option Level")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Total Working Years
```{r, echo = FALSE}

hist(ea$TotalWorkingYears, col = "#4AA4DE",breaks = 40, main = "Employee Total Working Years Distribution", xlab = "Total Working Years", border = FALSE)

barplot(table(ea$Attrition,ea$TotalWorkingYears), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Total Working Years", ylab = "Attrition", main = "Attrition base on Employee Total Working Years")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

Note: There is a abnormally large value 114 in this column.

We made a assumption that the 114 was a typo and it's suppose to be 14
```{r}

sort(ea$TotalWorkingYears, decreasing = TRUE)[1]

ea$DistanceFromHome[ea$DistanceFromHome == 114] <- 14

```

### Training Time Last Year
```{r, echo = FALSE}

hist(ea$TrainingTimesLastYear, col = "#4AA4DE",breaks = 6, main = "Employee Training Time Last Year Distribution", xlab = "Training Time Last Year", border = FALSE)

barplot(table(ea$Attrition,ea$TrainingTimesLastYear), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Training Time Last Year", ylab = "Attrition", main = "Attrition base on Employee Training Time Last Year")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Working Life Balance
```{r, echo = FALSE}

hist(ea$WorkLifeBalance, col = "#4AA4DE",breaks = 10, main = "Employee Working Life Balance Distribution", xlab = "Working Life Balance", border = FALSE)

barplot(table(ea$Attrition,ea$WorkLifeBalance), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Working Life Balance", ylab = "Attrition", main = "Attrition base on Employee Working Life Balance")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Years At Company
```{r, echo = FALSE}

hist(ea$YearsAtCompany, col = "#4AA4DE",breaks = 40, main = "Employee Years At Company Distribution", xlab = "Years At Company", border = FALSE)

barplot(table(ea$Attrition,ea$YearsAtCompany), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Years At Company", ylab = "Attrition", main = "Attrition base on Employee Years At Company")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Years In Current Role
```{r, echo = FALSE}

hist(ea$YearsInCurrentRole, col = "#4AA4DE",breaks = 20, main = "Employee Years In Current Role Distribution", xlab = "Years In Current Role", border = FALSE)

barplot(table(ea$Attrition,ea$YearsInCurrentRole), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Years In Current Role", ylab = "Attrition", main = "Attrition base on Employee Years In Current Role")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Years Since Last Promotion
```{r, echo = FALSE}

hist(ea$YearsSinceLastPromotion, col = "#4AA4DE",breaks = 15, main = "Employee Years Since Last Promotion Distribution", xlab = "Years Since Last Promotion", border = FALSE)

barplot(table(ea$Attrition,ea$YearsSinceLastPromotion), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Years Since Last Promotion", ylab = "Attrition", main = "Attrition base on Employee Years Since Last Promotion")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

### Years With Current Manager
```{r, echo = FALSE}

hist(ea$YearsWithCurrManager, col = "#4AA4DE",breaks = 200, main = "Employee Years With Current Manager Distribution", xlab = "Years With Current Manager", border = FALSE)

barplot(table(ea$Attrition,ea$YearsWithCurrManager), col = c("#4AA4DE","gray"),border = FALSE,xlab = "Years With Current Manager", ylab = "Attrition", main = "Attrition base on Employee Years With Current Manager")
legend("topright", levels(ea$Attrition), fill = c("#4AA4DE","gray"), border = FALSE, bty = "n")

```

Note: There is a abnormally large value 219 in this column.

we made an assumption that the 219 was a type and because that employee spent 20 years at the company so it's suppose to be 19
```{r}

sort(ea$YearsWithCurrManager, decreasing = TRUE)[1]

ea$YearsWithCurrManager[ea$YearsWithCurrManager == 219] <- 19

```

## {-}

# **Association Rule Mining**
### Turn Numerical Variables into Categorical Varisbles

```{r}
ea$Age<-arules::discretize(ea$Age, breaks = 3,labels = c("Younger-Age","Mid-Age","Older-Age"),method = "frequency")
ea$Age<-as.factor(ea$Age)

```

```{r}

ea$Attrition<-as.factor(ea$Attrition)

```

```{r}

ea$BusinessTravel<-as.factor(ea$BusinessTravel)

```

```{r}
ea$DailyRate<-arules::discretize(ea$DailyRate, breaks = 3,labels = c("Low","Medium","High"),method = "frequency")
ea$DailyRate<-as.factor(ea$DailyRate)

```

```{r}

ea$Department<-as.factor(ea$Department)

```

```{r}
ea$DistanceFromHome<-arules::discretize(ea$DistanceFromHome, breaks = 3,labels = c("Near","Medium","Far"),method = "frequency")
ea$DistanceFromHome<-as.factor(ea$DistanceFromHome)

```

```{r}
ea$Education<-arules::discretize(ea$Education, breaks = 4,labels = c("Poor Educated", "Basic Educated", "Well Educated", "Excellent Educated"),method = "frequency")
ea$Education<-as.factor(ea$Education)

```

```{r}

ea$EducationField<-as.factor(ea$EducationField)

```

```{r}
ea$EnvironmentSatisfaction<-arules::discretize(ea$EnvironmentSatisfaction, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$EnvironmentSatisfaction<-as.factor(ea$EnvironmentSatisfaction)

```

```{r}

ea$Gender<-as.factor(ea$Gender)

```

```{r}
ea$HourlyRate<-arules::discretize(ea$HourlyRate, breaks = 3,labels = c("Low","Medium","High"),method = "frequency")
ea$HourlyRate<-as.factor(ea$HourlyRate)

```

```{r}
ea$JobInvolvement<-arules::discretize(ea$JobInvolvement, breaks = 3,labels = c("Low","Medium","High"),method = "interval")
ea$JobInvolvement<-as.factor(ea$JobInvolvement)

```

```{r}
ea$JobLevel<-arules::discretize(ea$JobLevel, breaks = 3,labels = c("Junior Level", "Senior Level", "Manager Level"),method = "interval")
ea$JobLevel<-as.factor(ea$JobLevel)

```

```{r}

ea$JobRole<-as.factor(ea$JobRole)

```

```{r}
ea$JobSatisfaction<-arules::discretize(ea$JobSatisfaction, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$JobSatisfaction<-as.factor(ea$JobSatisfaction)

```

```{r}

ea$MaritalStatus<-as.factor(ea$MaritalStatus)

```

```{r}
ea$MonthlyIncome<-arules::discretize(ea$MonthlyIncome, breaks = 3,labels = c("Low","Medium","High"),method = "frequency")
ea$MonthlyIncome<-as.factor(ea$MonthlyIncome)

```

```{r}
ea$MonthlyRate<-arules::discretize(ea$MonthlyRate, breaks = 3,labels = c("Low","Medium","High"),method = "frequency")
ea$MonthlyRate<-as.factor(ea$MonthlyRate)

```

```{r}
ea$NumCompaniesWorked<-arules::discretize(ea$NumCompaniesWorked, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$NumCompaniesWorked<-as.factor(ea$NumCompaniesWorked)

```

```{r}
ea$PercentSalaryHike<-arules::discretize(ea$PercentSalaryHike, breaks = 3,labels = c("Low","Medium","High"),method = "frequency")
ea$PercentSalaryHike<-as.factor(ea$PercentSalaryHike)

```

```{r}
ea$PerformanceRating<-arules::discretize(ea$PerformanceRating, breaks = 2,labels = c("low", "high"),method = "interval")
ea$PerformanceRating<-as.factor(ea$PerformanceRating)

```

```{r}
ea$RelationshipSatisfaction<-arules::discretize(ea$RelationshipSatisfaction, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$RelationshipSatisfaction<-as.factor(ea$RelationshipSatisfaction)

```

```{r}
ea$StockOptionLevel<-arules::discretize(ea$StockOptionLevel, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$StockOptionLevel<-as.factor(ea$StockOptionLevel)

```

```{r}
ea$TotalWorkingYears<-arules::discretize(ea$TotalWorkingYears, breaks = 2,labels = c("short", "long"),method = "frequency")
ea$TotalWorkingYears<-as.factor(ea$TotalWorkingYears)

```

```{r}
ea$TrainingTimesLastYear<-arules::discretize(ea$TrainingTimesLastYear, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$TrainingTimesLastYear<-as.factor(ea$TrainingTimesLastYear)

```

```{r}
ea$WorkLifeBalance<-arules::discretize(ea$WorkLifeBalance, breaks = 2,labels = c("low", "high"),method = "frequency")
ea$WorkLifeBalance<-as.factor(ea$WorkLifeBalance)

```

```{r}
ea$YearsAtCompany<-arules::discretize(ea$YearsAtCompany, breaks = 2,labels = c("short", "long"),method = "frequency")
ea$YearsAtCompany<-as.factor(ea$YearsAtCompany)

```

```{r}
ea$YearsInCurrentRole<-arules::discretize(ea$YearsInCurrentRole, breaks = 2,labels = c("short", "long"),method = "frequency")
ea$YearsInCurrentRole<-as.factor(ea$YearsInCurrentRole)

```

```{r}
ea$YearsSinceLastPromotion<-arules::discretize(ea$YearsSinceLastPromotion, breaks = 2,labels = c("short", "long"),method = "frequency")
ea$YearsSinceLastPromotion<-as.factor(ea$YearsSinceLastPromotion)

```

```{r}
ea$YearsWithCurrManager<-arules::discretize(ea$YearsWithCurrManager, breaks = 2,labels = c("short", "long"),method = "frequency")
ea$YearsWithCurrManager<-as.factor(ea$YearsWithCurrManager)

```

## Run Association Rule Mining Algorithm {.tabset .tabset-pills}
### Baseline Model
When Attrition = Yes
```{r}
fac_var <- sapply(ea, is.factor)

ea_trans <- as(ea[,fac_var], "transactions")

Attrition_Yes <- apriori(data = ea_trans, parameter = list(support = 0.01, confidence = 0.5), 
                         appearance = list(default = "lhs", rhs = c("Attrition=Yes")))
```

```{r}

Attrition_Yes<-head(sort(Attrition_Yes,decreasing = T,by="lift"),5)

inspect(head(sort(Attrition_Yes, by = "lift", descreasing = T), 5))

```
Plot the association rules with Attrition = Yes
```{r}

plot(Attrition_Yes,method="graph")
print("Top 5 rules predict who leave:", inspect(head(sort(Attrition_Yes, by = "lift", descreasing = T), 5))[,1])

```

When Attrition = No
```{r}

Attrition_No <- apriori(data = ea_trans, parameter = list(support = 0.01, confidence = 0.5), 
                         appearance = list(default = "lhs", rhs = c("Attrition=No")))
```

```{r}

Attrition_No<-head(sort(Attrition_No,decreasing = T,by="lift"),5)

inspect(head(sort(Attrition_No, by = "lift", descreasing = T), 5))

```
Plot the association rules with Attrition = No
```{r}

plot(Attrition_No,method="graph")
print("Top 5 rules predict who stay:", inspect(head(sort(Attrition_No, by = "lift", descreasing = T), 5))[,1])

```

### Fine Tuned Mode
When Attrition = Yes

```{r}
fac_var <- sapply(ea, is.factor)

ea_trans <- as(ea[,fac_var], "transactions")

Attrition_Yes <- apriori(data = ea_trans, parameter = list(support = 0.01, confidence = 0.3), 
                         appearance = list(default = "lhs", rhs = c("Attrition=Yes")))
```

```{r}

Attrition_Yes<-head(sort(Attrition_Yes,decreasing = T,by="lift"),5)

inspect(head(sort(Attrition_Yes, by = "lift", descreasing = T), 5))

```
Plot the association rules with Attrition = Yes
```{r}

plot(Attrition_Yes,method="graph")
print("Top 5 rules predict who leave:", inspect(head(sort(Attrition_Yes, by = "lift", descreasing = T), 5))[,1])
```

When Attrition = No
```{r}

Attrition_No <- apriori(data = ea_trans, parameter = list(support = 0.01, confidence = 0.3), 
                         appearance = list(default = "lhs", rhs = c("Attrition=No")))
```

```{r}

Attrition_No<-head(sort(Attrition_No,decreasing = T,by="lift"),5)

inspect(head(sort(Attrition_No, by = "lift", descreasing = T), 5))

```
Plot the association rules with Attrition = No
```{r}

plot(Attrition_No,method="graph")
print("Top 5 rules predict who stay:", inspect(head(sort(Attrition_No, by = "lift", descreasing = T), 5))[,1])

```



